Test susieI using whole genome, s40.22 samples

### 2020-12-03 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
indididual level pipeline

>>>>

## Select block + susieI (3)
* Regions: all regions 5 iterations. Then filter out regions with probability of having two or more effects > 0.2 to estimate paramters 20 iterations. then all regions to get all PIP. LD-defined regions.
* Susie run parameters: `L=1`. We estimate prior variance based on EM and plug into SUSIE. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5. We use null weight when run susie. We run 5 iterations. Then filter out regions with probability of having two or more effects. Then rerun on selected regions to estimate parameters (20 iterations). Lastly, run on all regions with `L=5` to get PIP.

```{r param3susiefl, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config16.fl.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config16.fl.susieI.txt")

```{r pip3susiefl, fig.height=6, fig.width=8}
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config16.flrerun.susieI.txt")
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

## Select block + susieI (4)
* Regions: all regions 5 iterations. Then filter out regions with probability of having two or more effects > 0.1 to estimate paramters 20 iterations. then all regions to get all PIP. LD-defined regions.
* Susie run parameters: `L=1`. We estimate prior variance based on EM and plug into SUSIE. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5. We use null weight when run susie. We run 5 iterations. Then filter out regions with probability of having two or more effects. Then rerun on selected regions to estimate parameters (20 iterations). Lastly, run on all regions with `L=5` to get PIP.

```{r param4susiefl, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config17.fl.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config17.fl.susieI.txt")

```{r pip4susiefl, fig.height=6, fig.width=8}
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config17.flrerun.susieI.txt")
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)")
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)")
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```
